---
title: "Example application"
author: "Sophie Meakin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE, message = FALSE,
  out.width = "100%", fig.width = 14, fig.height = 9,
  comment = "#>"
)
devtools::load_all()  # library(pepbp)
library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
```

In this example we use *pepbp* to quantify the impact of post-exposure prophylaxis (PEP) for high-risk contacts on outbreak control. Specifically, we consider how the probability of receiving PEP and the effectiveness of PEP affect the size of outbreaks, the average number of secondary cases (R0), and the number of PEP doses required.

## Model

First, we define a grid of scenarios for the parameters of interest:

-   Probability that a high-risk contact receives PEP = {0.2, 0.6, 1};
-   Effectiveness of PEP (relative risk of becoming a case) = {0, 0.1, 0.2, ..., 0.9, 1}.

All other parameters are fixed. The mean number of high-risk contacts is 2 and the probability that each high-risk contact becomes a case (without PEP) is 0.75. The mean number of low-risk contacts is 5 and the probability that each low-risk contact becomes a case is 0.1.

```{r}
scenario_grid <- expand_grid(
  # Varying parameters
  prop_pep = seq(0.2, 1, 0.4),
  rel_risk = seq(0, 1, 0.1),
  # Fixed parameters
  n_initialcases = 5,
  hrc_mu = 2,
  hrc_disp = 1,
  lrc_mu = 5,
  lrc_disp = 10,
  p_hrc_case = 0.75,
  p_lrc_case = 0.1
) %>%
  mutate(scenario = 1:n()) %>%
  select(scenario, everything())
```

Now run the 100 iterations of the branching process model for each scenario, and summarise the results:

```{r}
res <- parameter_sweep(
  scenarios = scenario_grid,
  n_sim = 100,
  sim_fn = partial(scenario_sim, cap_max_gen = 5, cap_max_cases = 2500)
)

res_summary <- summarise_results(res) %>%
  group_by(scenario) %>%
  mutate(big50 = sum(outbreak_size > 50)/n()) %>%
  right_join(scenario_grid, by = "scenario") %>%
  ungroup()
```

## Results

### Effect of PEP on preventing large outbreaks

```{r}
res_summary %>%
  filter(prop_pep > 0) %>%
  select(scenario, prop_pep, rel_risk, big50) %>%
  distinct() %>%
  ggplot(aes(x = rel_risk, y = big50, col = as.factor(prop_pep))) +
  geom_point(size = 3) +
  geom_line() +
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  scale_color_brewer(palette = "Reds") +
  labs(
    x = "Relative risk of HRCs becoming a case (PEP vs. no PEP)", y = "Proportion of outbreaks with at least 50 cases",
    col = "Probability of receiving PEP"
  ) +
  theme_bw() +
  theme(text = element_text(size = 16), legend.position = "top")
```

### Effect of PEP on R0 in large outbreaks

```{r}
plot_r0(res_summary[which(res_summary$outbreak_size > 50),])
```

### Number of PEP doses required

```{r}
res_summary %>%
  filter(prop_pep > 0) %>%
  group_by(scenario, n_initialcases, prop_pep, rel_risk) %>%
  summarise(
    npep_mean = mean(n_pep),
    npep_median = median(n_pep),
    npep_q025 = quantile(n_pep, 0.025),
    npep_q25 = quantile(n_pep, 0.25),
    npep_q75 = quantile(n_pep, 0.75),
    npep_q975 = quantile(n_pep, 0.975),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = rel_risk, col = as.factor(prop_pep))) +
  geom_ribbon(aes(ymin = npep_q25, ymax = npep_q75, fill = as.factor(prop_pep)), col = NA, alpha = 0.4) +
  geom_point(aes(y = npep_mean), size = 3) +
  geom_line(aes(y = npep_mean)) +
  scale_x_continuous(breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, NA)) +
  scale_color_brewer(palette = "Reds") +
  scale_fill_brewer(palette = "Reds") +
  labs(
    x = "Relative risk of becoming a case", y = "Number of PEP doses",
    col = "Probability of receiving PEP", fill = "Probability of receiving PEP"
  ) +
  theme_bw() +
  theme(text = element_text(size = 16), legend.position = "top")
```
